---
---
# Basic facts about Pladias

**History**

* project started on 2014, first launch 2016 - instance for vascular plants of the Czech Republic [Pladias](pladias.ibot.cas.cz)
* 2019 new instance for nonvascular plants of the Czech Republic [DaLiBor](https://dalibor.ibot.cas.cz) 
* 2021 new instance for vegetation traits (having no occurrence data included) [CEVS](https://cevs.ibot.cas.cz)
* 2024 new instance for vascular plants of the Slovakia [Pladias.sk](https://pladias.sav.sk/)

**Technology stack**

* PostgreSQL + PostGIS + PostgREST
* Java with Play! Framework
* Geoserver

**Misc**





## Trait data

TBD

## Occurrence data
The main amount of the records is comming from individual external data providers in the Czech Republic (Pladias as a secondary resource), only minority is imported to the Pladias as a primary storage. 

```{r}
query <- "WITH d AS (SELECT p.institution_id, p.name as project, COUNT(*) 
                FROM atlas.records r 
                JOIN atlas.projects p ON (p.id=r.project_id)                
                GROUP BY p.id)
                SELECT d.project, i.name, d.count FROM d JOIN  public.institutions i ON (i.id=d.institution_id)  ORDER BY d.count DESC"
data <- dbGetQuery(db, query)

data$project <- factor(data$project, levels = unique(data$project))
 
data %>%
    kable(caption = "Records insitutional origin") %>%
    kable_styling(full_width = F)
```

### Validity status
For description of the record validity, a four-level classification is used (so called "semafor"). Using priority, the final interpretation of the occurrence status for taxon-quadrant is derived. 


```{r, include=FALSE}
query <- "SELECT s.description as name, s.color, COUNT(*), s.priority FROM atlas.records r JOIN atlas.record_validation_status s ON (s.id=r.validation_status) GROUP BY s.id ORDER BY s.priority DESC"
data <- dbGetQuery(db, query)

data$name <- factor(data$name, levels = unique(data$name))
 
table <- data %>%
    mutate(
    color_code = paste0("<span style='background-color:", color, ";'>&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;</span>"),
    count = format(count, big.mark = " ", decimal.mark = ","),
    ) %>%
    select(-color) %>%
    kable("html", escape = F, caption = "Records count according to the status of validity") %>%
    kable_styling(full_width = F)

plot <- ggplot(data, aes(x = name, y = count, fill = color)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_identity() +
  labs(title = "Records count according to the status of validity",
       x = "Status (called semafor)",
       y = "Records count") +
   theme(
       axis.text = element_text(size = 15),
       axis.title = element_text(size = 16),
       plot.title = element_text(size = 18, face = "bold")
       )
```
<div style="display: flex; justify-content: space-between;">
<div style="width: 30%;">
```{r }
    table
```
</div>
<div style="width: 30%;">
&nbsp;
</div>
<div>
```{r }
    plot
```
</div>
</div>

### Native status

```{r, include=FALSE}
query <- "SELECT s.name_cz as name, COUNT(*), s.priority FROM atlas.records r JOIN atlas.record_originality_status s ON (s.id=r.originality_id) GROUP BY s.id ORDER BY s.priority DESC"
data <- dbGetQuery(db, query)

data$name <- factor(data$name, levels = unique(data$name))

table <- data %>%
    kable("html", escape = F, caption = "Records count according to the originality status") %>%
    kable_styling(full_width = F)

plot <- ggplot(data, aes(x = name, y = count)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_identity() +
  labs(title = "Records count according to the originality status",
       x = "Status",
       y = "Records count") +
   theme(
       axis.text = element_text(size = 15),
       axis.title = element_text(size = 16),
       plot.title = element_text(size = 18, face = "bold")
       )
```
<div style="display: flex; justify-content: space-between;">
<div style="width: 30%;">
```{r }
    table
```
</div>
<div style="width: 30%;">
&nbsp;
</div>
<div>
```{r }
    plot
```
</div>
</div>

### Copyright
There are multiple record licence options available as shown in the table. In the near future, we will transfer P-P-P records to CC-BY-4.0.

 ```{r, include=FALSE}

query1 <- "SELECT * FROM public.licenses ORDER BY id DESC"
data1 <- dbGetQuery(db, query1)

table1 <- data1 %>%
  kable(caption = "Licenses available") %>%
  kable_styling(full_width = F)

 query2 <- "SELECT l.key, l. description, COUNT(*)
           FROM atlas.records r
           JOIN public.licenses l ON (l.id=r.license_id)
           GROUP BY l.id ORDER BY l.id DESC"
 data2 <- dbGetQuery(db, query2)

 table2 <- data2 %>%
     kable(caption = "Usage of licenses") %>%
     kable_styling(full_width = F)

 ```

<div style="display: flex; justify-content: space-between;">
<div style="width: 70%;">
```{r }
    table1
```
</div>
<div style="width: 40%;">
&nbsp;
</div>
<div>
```{r }
    table2
```
</div>
</div>